### 2021-07-13 src/paper.tex
Add science style.
Went through paper once.

\input{templates/Preamble_Page_layout_general}
\input{templates/Preamble_Page_layout_paper}
\subimport{templates/}{Preamble_Fonts_Charter_FiraSans}
\input{templates/Preamble_Sansserif_math}
\input{templates/Preamble_BibLaTeX_AER}
%\input{templates/Preamble_BibLaTeX_APA}
\input{templates/Preamble_Commenting_and_highlighting}
\input{templates/Preamble_Miscellaneous}

@@

@@

    This paper aims to be completely reproducible. The code for the general model can be
    found at
    \href{https://github.com/covid-19-impact-lab/sid/}{https://github.com/covid-19-impact-lab/sid/}
    and its documentation at
    \href{https://sid-dev.readthedocs.io/en/latest/}{https://sid-dev.readthedocs.io/en/latest/}.
    The code for the application to Germany can be found at
    \href{https://github.com/covid-19-impact-lab/sid-germany/}{https://github.com/covid-19-impact-lab/sid-germany/}
    with a very rudimentary documentation at
    \href{https://sid-germany.readthedocs.io/en/latest/}{https://sid-germany.readthedocs.io/en/latest/}.

>>>>

\input{templates/Preamble_Page_layout_general}
\input{templates/Preamble_Page_layout_paper}
\subimport{templates/}{Preamble_Fonts_Charter_FiraSans}
\input{templates/Preamble_Sansserif_math}
% \input{templates/Preamble_BibLaTeX_AER}
% \input{templates/Preamble_BibLaTeX_APA}
\input{templates/Preamble_BibLaTeX_Science}
\input{templates/Preamble_Commenting_and_highlighting}
\input{templates/Preamble_Miscellaneous}

@@

\tableofcontents

@@

### 2021-07-13 src/paper/data/course_of_disease.tex
Went through paper once.

\subsection{Medical Parameters}
\label{sec:medical_params}

This section discusses the medical parameters used in the model, their sources and how
we arrived at the distributions used in the model.\footnote{Additional information can
be found in the
\href{https://sid-dev.readthedocs.io/en/latest/reference_guides/epi_params.html}{online
documentation}.} See Figure~\ref{fig:model_disease_progression} for a summary of our
disease progression model.

@@

% Latency Period
The first medical parameter we need is the distribution of the length of the period
between infection and the start of infectiousness, the so called latent period,
$\gamma_{infectious}$. \cite{Zhao2021} estimate the latent period to last 3.3 days (95\%
CI: 0.2, 7.9). In line with this estimate our latent period lasts one to five days with a
slightly lower average of two days.

% Asymptomatic Share
Once individuals become infectious a share of them goes on to develop symptoms while
others remain asymptomatic. We rely on data by \cite{Davies2020} for the age-dependent
probability to develop symptoms. It varies from 25\% for children and young adults to
nearly 70\% for the elderly.
% Length of the presymptomatic stage
Similar to \citet{Peak2020} and in line with \citet{He2020} we set the length of the
presymptomatic stage of age group $a$, $\gamma_{symptoms,\:a}$ to be one or two days. The
probability to become symptomatic for age group $a$ is split equally between one and two
days. This combined with our latency period leads to an incubation period that is in line
with the meta analysis by \citet{McAloon2020}.

>>>>

\subsection{Course of Disease}
\label{sub:data_course_of_disease}

This section discusses the parameters governing the course of disease, their sources and
how we arrived at the distributions used in the paper.\footnote{Additional information
can be found in the
\href{https://sid-dev.readthedocs.io/en/latest/reference_guides/epi_params.html}{online
documentation}.} See Figure~\ref{fig:model_disease_progression} for a summary of our
disease progression model.

@@

% Latency Period
We denote the latent period---i.e., the time span between infection and the start of
infectiousness---by $\gamma_{infectious}$. \cite{Zhao2021} estimate the latent period to
last 3.3 days (95\% CI: 0.2, 7.9) on average. In line with this estimate our latent
period lasts one to five days.

% Asymptomatic Share
Once individuals become infectious, a share of them goes on to develop symptoms while
others remain asymptomatic. We rely on data by \cite{Davies2020} for the age-dependent
probability to develop symptoms. It varies from 25\% for children and young adults to
nearly 70\% for the elderly.
% Length of the presymptomatic stage
Similar to \citet{Peak2020} and in line with \citet{He2020} we set the length of the
presymptomatic stage of age group $a$, $\gamma_{symptoms,\:a}$ to be one or two days. The
probability to become symptomatic for age group $a$ is split equally between one and two
days. This combined with our latency period leads to an incubation period that is in line
with the meta analysis by \citet{McAloon2020}.

### 2021-07-13 src/paper/data/synthetic_population.tex
Improve wording of number of contacts in the model section.
Add parameter notation, shorten sentences and fix some wordings in the fit section.
Went through paper once.

Lastly, for the distribution of vaccinations every individual is assigned a vaccination
group and a vaccination rank from that group that creates a complete vaccination queue
over the population including a share that refuses to be vaccinated ($\xi$) which we
calibrate to  15\% \citep{RKI2021c}. The vaccination groups are created to match the
recommendations by the Ständige Impfkommission \citep{VygenBonnet2020}.\footnote{We cover
that teachers were prioritized more than recommended by the commission.} To cover that
the Pfizer-BioNTech vaccine was later approved for younger age groups we put adolescents
and children into two groups that follow after the general population. These groups do
not become eligible within our simulation frame until June. The way vaccinations are
rolled out in our model is shown in Figure~\ref{fig:vaccinations_by_age_group}.

\begin{figure}[ht]   % vaccinations by age group
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/vaccinations/spring_baseline}
  \caption{Vaccination Rates by Age Group}
  \floatfoot{\noindent \textit{Note:} An individual's vaccination priority depends on her
  work contact priority, her age group and a random component to capture medical
  preconditions like diabetes. 15\% of the population refuse to be vaccinated ($\xi$).
  Adolescents would be vaccinated after the general population and children last. The
  figure clearly shows that the first vaccinations go to some workers with very high work
  contact priority and to the 80 to 100 age group followed by the 60 to 79 year olds.
  Both groups are saturated with vaccinations by mid March and start of May respectively.
  By June a third of the younger adults have received the vaccination but these groups
  still remain far from herd immunity thresholds.}
  \label{fig:vaccinations_by_age_group}
\end{figure}

>>>>

% vaccination rank
Lastly, for the distribution of vaccinations every individual is assigned a vaccination
group and a vaccination rank from that group that creates a complete vaccination queue
over the population including a share that refuses to be vaccinated ($\xi$) which we
calibrate to  15\% \citep{RKI2021c}. The vaccination groups are created to match the
recommendations by the Ständige Impfkommission \citep{VygenBonnet2020}.\footnote{We cover
that teachers were prioritized more than recommended by the commission.} To cover that
the Pfizer-BioNTech vaccine was later approved for younger age groups we put adolescents
and children into two groups that follow after the general population. These groups do
not become eligible within our simulation frame until June. The way vaccinations are
rolled out in our model is shown in Figure~\ref{fig:vaccinations_by_age_group}.

\begin{figure}[ht]   % vaccinations by age group
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/vaccinations/spring_baseline}
  \caption{Vaccination Rates by Age Group}
  \floatfoot{\noindent \textit{Note:} An individual's vaccination priority depends on her
  work contact priority, her age group and a random component to capture
  preconditions like diabetes. 15\% of the population refuse to be vaccinated ($\xi$).
  Adolescents would be vaccinated after the general population and children last. The
  figure clearly shows that the first vaccinations go to some workers with very high work
  contact priority and to the 80 to 100 age group followed by the 60 to 79 year olds.
  Both groups are saturated with vaccinations by mid March and start of May respectively.
  By June a third of the younger adults have received the vaccination but these groups
  still remain far from herd immunity thresholds.}
  \label{fig:vaccinations_by_age_group}
\end{figure}

### 2021-07-13 src/paper/literature_review.tex
Went through paper once.

The workhorse model in epidemiology is the SEIR model. However,
The traditional SEIR model is not fine-grained enough to model nuanced policies. This
has motivated a large number of researchers to extend the standard model to allow for
more heterogeneity and flexibility. Examples are \citet{Grimm2020},
\citet{Donsimoni2020} and \citet{Acemoglu2020} who develop multi group SEIR models to
analyze the effects of targeted lockdowns and \citet{Berger2020} who extend the SEIR
model to analyze testing and conditional quarantines. For a more comprehensive review
see \citet{Avery2020}. Others have used the results of a standard SEIR model as input
for economic models that estimate the cost of policies (e.g. \citet{Dorn2020}).

@@

The OpenABM-Covid-19 model by \citet{Hinch2020} is the closest in spirit to ours. They
model detailed contact networks for workplaces, schools and households and can evaluate
the effect of several NPIs. The main focus of their application are contact tracing
policies.

@@

\citet{Bicher2021} implement a model that simulates the complete Austrian population
with almost nine million people. It uses the same data provided by \citet{Mossong2008}
as we use to calibrate contact networks for households, workplaces and schools. The
model focuses and analyzing the effect of different contact tracing strategies. It is
calibrated with data from the first wave (February 21 to April 9).

Moreover, there are several forthcoming applications of agent-based simulation models
with contact networks. Examples are \citet{Basurto2020}, \citet{DelliGatti2020} and
\citet{Mellacher2020}.

>>>>

The workhorse model in epidemiology is the SEIR model. However, The traditional SEIR
model is not fine-grained enough to model nuanced policies.\comment[id=HM]{Still old
motivation. Hard to get the timing of tests and results right?} This has motivated a
large number of researchers to extend the standard model to allow for more heterogeneity
and flexibility. Examples are \citet{Grimm2020}, \citet{Donsimoni2020} and
\citet{Acemoglu2020}\comment[id=HM]{We need to cite more strategically. Cut Grimm,
Donsinomi. More state of the art SEIR in other fields. Or drop SEIR altogether? If I
read that as a Michael Meyer-Hermann type, I would think, ``ah, these economists
again...''} who develop multi group SEIR models to analyze the effects of targeted
lockdowns and \citet{Berger2020} who extend the SEIR model to analyze testing and
conditional quarantines. For a more comprehensive review see \citet{Avery2020}. Others
have used the results of a standard SEIR model as input for economic models that
estimate the cost of policies (e.g. \citet{Dorn2020}).

@@

The OpenABM-Covid-19 model by \citet{Hinch2020} is the closest in spirit to
ours\comment[id=HM]{I'd rather be close to Aleta et al. ;-)}. They model detailed
contact networks for workplaces, schools and households and can evaluate the effect of
several NPIs. The main focus of their application are contact tracing policies.

@@

\citet{Bicher2021} simulate the Austrian population during the first wave (February 21
to April 9, 2020). It uses the same data provided by \citet{Mossong2008} as we use to
calibrate contact networks for households, workplaces and schools. The model focuses on
analyzing the effect of different contact tracing strategies.

Moreover, there are several forthcoming applications\comment[id=HM]{What is that
supposed to mean?} of agent-based simulation models with contact networks. Examples are
\citet{Basurto2020}, \citet{DelliGatti2020} and \citet{Mellacher2020}.

### 2021-07-13 src/paper/model/course_of_disease.tex
Went through paper once.

\subsection{Course of the Disease}
\label{sub:disease_progression}

The disease progression in the model is fairly standard. It is depicted in
Figure~\ref{fig:model_disease_progression} and the values and source of the relevant
parameters are describes in Section~\ref{sec:medical_params}.

@@

It would be easy to make the course of disease even more fine-grained. For example, we
could model people who require hospitalization but not intensive care. So far we opted
against that because only the intensive care capacities are feared to become a bottleneck
in Germany.

>>>>

\subsection{Course of Disease}
\label{sub:model_course_of_disease}

The disease progression in the model is fairly standard. It is depicted in
Figure~\ref{fig:model_disease_progression} and the values and source of the relevant
parameters are describes in Section~\ref{sub:data_course_of_disease}.

@@

% It would be easy to make the course of disease even more fine-grained. For example, we
% could model people who require hospitalization but not intensive care. So far we opted
% against that because only the intensive care capacities are feared to become a bottleneck
% in Germany.

### 2021-07-13 src/paper/report.tex
Use parameter notation everywhere in the data section.
Went through paper once.

The four contact networks are chosen so that the most common NPIs can be modeled in great
detail. NPIs affect the number of contacts or the risk of transmitting the disease upon
having physical contact. The effect of different NPIs will generally vary across contact
types. For example, a mandate to work from\comment[id=K]{$\rho_{attend,\,t}$} home will
reduce the number of work contacts to zero for a fraction of the working population.
Schools and daycare can be closed entirely, operate at reduced capacity---including an
alternating schedule---, or implement mitigation measures like masking requirements or
air filters \citep{Lessler2021}. Curfews\comment[id=K]{would enter into $\rho_{other\:,t}$} may reduce the number of contacts in
non-work/non-school/non-work settings. In any setting, measures like masking requirements
would reduce the probability of infection associated with a contact \citep{Cheng2021}.\comment[id=K]{$\rho_{hygiene}$}

@@

In the model, susceptibility to contracting the SARS-CoV-2 virus is dependent on
age\comment[id=K]{$\zeta_{a}$}. A possible infection progresses as shown in
Figure~\ref{fig:model_disease_progression}. We differentiate between an initial period of
infection without being infectious or showing symptoms, being infectious (presymptomatic
or asymptomatic), showing symptoms, requiring intensive care, and recovery or death
\citep[similar to][]{Grimm2021}.\comment[id=HM]{Need to look for non-economists} The
probabilities of transitioning between these states depend on age;\comment[id=K]{$\gamma$
for all transition probabilities} their duration is random within intervals calibrated to
the medical literature (for a detailed description see Section~\ref{sec:medical_params}).
Conditional on the type of contact, infectiousness is independent of age
\citep{Jones2021}.\comment[id=K]{would be $\beta_{c}$}

The model includes several other features, which are crucial to describe the evolution of
the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness\comment[id=K]{$\sigma_v$} can be introduced. Agents may receive a
vaccination. With a probability of 75\% \citep{Hunter2021}, vaccinated agents become
immune and they do not transmit the virus \citep{Petter2021, LevineTiefenbrun2021,
Pritchard2021}.\footnote{75\% is lower than what is usually reported for after the second
dose of the Biontech/Pfizer vaccine, which is most commonly used in Germany. We choose it
because our model neither includes booster shots, nor does it allow vaccinated
individuals who became immune to transmit the disease\citep{Petter2021,
LevineTiefenbrun2021, Pritchard2021}. If anything, these assumptions would overstate the
effect of vaccines for our study period. This would be different if a large fraction of
vaccinated individuals had received a second dose already.} During the vaccine roll-out,
priority may depend on age and occupation.\comment[id=K]{Maybe mention that we have
refusers?}

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
some days to be processed\comment[id=K]{$\gamma_{PCR,\:d}$ where $d=$ number of days} and
there are aggregate capacity constraints throughout. In contrast, rapid antigen tests
yield immediate results; after a phase-in period, all tests that are demanded will be
performed. Specificity\comment[id=K]{$p_{negative|not\:infected}$} and
sensitivity\comment[id=K]{"$p_{positive|infected,\;i,\:t}$", where $i$ is the individual
and $t$ is the date to determine time until/since infectiousness} of these tests is set
according to data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the
timing of the test relative to the onset of infectiousness.
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand. Schools may
require staff and students to be tested regularly.\comment[id=K]{"$\pi_{teacher,\:t}$"
etc. } Rapid tests may be offered by employers to on-site workers. Individuals may demand
tests for private reasons, which include having plans to meet other people, showing
symptoms of CoViD-19, and because a household member tested positively for the virus. We
endow each agent with an individual compliance parameter. This parameter determines
whether she takes up rapid tests.\footnote{A positive test result (of either kind), as
well as symptoms leads most individuals to reduce their contacts; this is why tests
impact the actual contacts in Figure~\ref{fig:model_description}.}

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
materials for an overview.} Contact diaries yield pre-pandemic distributions of contacts
for different contact types and their assortativity by age group\comment[id=K]{Should we
add all our sources here?}. Mobility data is used to model the evolution of work
contacts. School and daycare policies can be incorporated directly from official
directives. Administrative records on the number of tests, vaccinations by age and
region, and the prevalence of virus strains are generally available. Surveys may ask
about test offers, propensities to take them up, and past tests. Other studies' estimates
of the seasonality of infections can be incorporated directly. The remaining
parameters---most notably, these include infection probabilities by contact network and
the effects of some NPIs, see Supplementary Material~\ref{subsec:estimated_params}---will
be chosen numerically so that the model matches features of the data \citep[see][for the
general method, also described in Supplementary Material
\ref{subsec:estimated_param}]{McFadden1989}. In our application, we keep the number of
free parameters low in order to avoid overfitting. The data features to be matched
include official case numbers for each age group and region, deaths, and the share of the
B.1.1.7 strain.

The main issue with official case numbers is that they will contain only a fraction of
all infections. We thus model official cases as depicted in
Figure~\ref{fig:model_official_cases}. We take aggregate estimates of the share of
detected cases\comment[id=K]{$\psi$} and use data on the share of PCR tests administered
because of CoViD-19 symptoms\comment[id=K]{$\chi_{symptom}$}. As the share of
asymptomatic individuals varies by age group, this gives us age-specific shares (see
Figure~\ref{fig:share_known_cases_by_age_group} for the share of detected cases by age
group over time in our model). Our estimates suggest that---in the absence of rapid
testing---the detection rate is 80\% higher on average for individuals above age 80
compared to school age children. Once rapid test become available, confirmation of a
positive result\comment[id=K]{prob of demanding confirmation is $\chi_{confirmation}$} is
another reason leading to positive PCR tests.

@@

By March 2021, the set of policy instruments had become much more diverse. Around the
turn of the year, the first people were vaccinated with a focus on older age groups and
medical personnel (Figure~\ref{fig:antigen_tests_vaccinations}). Until the end of May,
43\% had received at least one dose of a vaccine. In late 2020, rapid tests started to
replace regular PCR tests for staff in many medical and nursing facilities. These had to
be administered by medical doctors or in pharmacies. At-home tests approved by
authorities became available in mid-March, rapid test centers were opened, and one test
per person and week was made available free of charge. In several states, customers were
only allowed to enter certain stores with a recent negative rapid test result. These
developments are characteristic of many countries: The initial focus on NPIs to slow the
spread of the disease has been accompanied by vaccines and a growing acceptance and use
of rapid tests. At broadly similar points in time, novel strains of the virus have
started to pose additional challenges.

@@

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations and rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections with only one channel active, the
final level is always the highest in case of the vaccination campaign (orange lines). The
Shapley value decomposition shows that vaccinations contribute 16\% to the cumulative
difference between scenarios. Reasons for this are the slow start---it took until
March~24th until 10\% of the population had received their first vaccination, the 20\%
mark was reached on April 19th---and the focus on older individuals. These groups
contribute less to the spread of the disease than others due to a lower number of
contacts (see Supplementary
Material~\ref{subsec:assortativity}).\comment[id=K]{Assortativity is the wrong section
here. They have few contacts in our model because they tend to live in small households
and don't have work or educ contacts. They are also more likely to meet other old people
but that's a different channel from what is written in the text.} By the end of our study
period, when first-dose vaccination rates reached around 40\% of the population, the
numbers of new cases would have started to decline. It is important to note that the
initial focus of the campaign was to prevent deaths and severe disease. Indeed, the case
fatality was rate considerably lower during the third wave when compared to the second
(4.4\% between October and February and 1.4\% between March and the end of
May).\comment[id=K]{This needs a source.}

>>>>

The four contact networks are chosen so that the most common NPIs can be modeled in
great detail. NPIs affect the number of contacts or the risk of transmitting the disease
upon having physical contact. The effect of different NPIs will generally vary across
contact types. For example, a mandate to work from\comment[id=K]{$\rho_{attend,\,t}$}
home will reduce the number of work contacts to zero for a fraction of the working
population. Schools and daycare can be closed entirely, operate at reduced
capacity---including an alternating schedule---, or implement mitigation measures like
masking requirements or air filters \citep{Lessler2021}. Curfews\comment[id=K]{would
enter into $\rho_{other\:,t}$} may reduce the number of contacts in settings outside of
work and school. In any setting, measures like masking requirements would reduce the
probability of infection associated with a contact
\citep{Cheng2021}.\comment[id=K]{$\rho_{hygiene}$}

@@

In the model, susceptibility to contracting the SARS-CoV-2 virus is dependent on
age\comment[id=K]{$\zeta_{a}$}. A possible infection progresses as shown in
Figure~\ref{fig:model_disease_progression}.\comment[id=HM]{New version of figure has
lost the timing. Need to explain d-subscript, maybe even better to add stuff like 1-3
days back in? Needs to be comprehensible without recurring to appendix} We differentiate
between an initial period of infection without being infectious or showing symptoms,
being infectious (presymptomatic or asymptomatic), showing symptoms, requiring intensive
care, and recovery or death \citep[similar to][]{Grimm2021}.\comment[id=HM]{Need to look
for non-economists -- this must be fairly standard?} The probabilities of transitioning
between these states depend on age; their duration is random and calibrated to medical
literature (for a detailed description see Section~\ref{sub:data_course_of_disease}).
Conditional on the type of contact, infectiousness is independent of age
\citep{Jones2021}.\comment[id=K]{would be $\beta_{c}$}

The model includes several other features, which are crucial to describe the evolution
of the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness\comment[id=K]{$\sigma_v$} can be introduced. Agents may receive a
vaccination. With a probability of 75\% \citep{Hunter2021}, vaccinated agents become
immune and they do not transmit the virus \citep{Petter2021, LevineTiefenbrun2021,
Pritchard2021}.\footnote{75\% is lower than what is usually reported for after the
second dose of the Biontech/Pfizer vaccine, which is most commonly used in Germany. We
choose it because our model neither includes booster shots, nor does it allow vaccinated
individuals who became immune to transmit the disease\citep{Petter2021,
LevineTiefenbrun2021, Pritchard2021}. If anything, these assumptions would overstate the
effect of vaccines for our study period. This would be different if a large fraction of
vaccinated individuals had received a second dose already.} During the vaccine roll-out,
priority may depend on age and occupation; some individuals will refuse vaccination
offers.

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
at least one day to be processed\comment[id=K]{$\gamma_{PCR,\:d}$ where $d=$ number of
days} and there are aggregate capacity constraints. In contrast, rapid antigen tests
yield immediate results; after a phase-in period, all tests that are demanded will be
performed. Specificity\comment[id=K]{$p_{negative|not\:infected}$} and
sensitivity\comment[id=K]{"$p_{positive|infected,\;i,\:t}$", where $i$ is the individual
and $t$ is the date to determine time until/since infectiousness} of these tests is set
according to data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the
timing of the test relative to the onset of infectiousness.
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand. Schools may
require staff and students to be tested regularly.\comment[id=K]{"$\pi_{teacher,\:t}$"
etc. } Rapid tests may be offered by employers to on-site workers. Individuals may
demand tests for private reasons, which include having plans to meet other people,
showing symptoms of CoViD-19, and because a household member tested positively for the
virus. We endow each agent with an individual compliance parameter. This parameter
determines whether she takes up rapid tests.\footnote{A positive test result (of either
kind), as well as symptoms leads most individuals to reduce their contacts; this is why
tests impact the actual contacts in Figure~\ref{fig:model_description}.}

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
materials for the precise sources.} Contact diaries yield pre-pandemic distributions of
contacts for different contact types and their assortativity by age group. Mobility data
is used to model the evolution of work contacts. School and daycare policies can be
incorporated directly from official directives. Administrative records on the number of
tests, vaccinations by age and region, and the prevalence of virus strains are generally
available. Surveys may ask about test offers, propensities to take them up, and past
tests. Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, these include infection probabilities
by contact network and the effects of some NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data \citep[see][for the general method, also described in
Supplementary Material \ref{subsec:estimated_params}]{McFadden1989}. In our application,
we keep the number of free parameters low in order to avoid overfitting. The data
features to be matched include official case numbers for each age group and region,
deaths, and the share of the B.1.1.7 strain.

The main issue with official case numbers is that they will contain only a fraction of
all infections. We thus model official cases as depicted in
Figure~\ref{fig:model_official_cases}\comment[id=HM]{Replace P2, P(compliance) by
symbols in figure}. We take aggregate estimates of the share of detected
cases\comment[id=K]{$\psi$} and use data on the share of PCR tests administered because
of CoViD-19 symptoms\comment[id=K]{$\chi_{symptom}$}. As the share of asymptomatic
individuals varies by age group, this gives us age-specific shares (see
Figure~\ref{fig:share_known_cases_by_age_group} for the share of detected cases by age
group over time in our model). Our estimates suggest that---in the absence of rapid
testing---the detection rate is 80\% higher on average for individuals above age 80
compared to school age children. Once rapid test become available, confirmation of a
positive result\comment[id=K]{prob of demanding confirmation is $\chi_{confirmation}$}
is another reason leading to positive PCR tests.

@@

By March 2021, the set of policy instruments had become much more diverse. Around the
turn of the year, the first people were vaccinated with a focus on older age groups and
medical staff (Figure~\ref{fig:antigen_tests_vaccinations}). Until the end of May, 43\%
had received at least one dose of a vaccine. In late 2020, rapid tests started to
replace regular PCR tests for staff in many medical and nursing facilities. These had to
be administered by medical doctors or in pharmacies. At-home tests approved by
authorities became available in mid-March, rapid test centers were opened, and one test
per person and week was made available free of charge. In several states, customers were
only allowed to enter certain stores with a recent negative rapid test result. These
developments are characteristic of many countries: The initial focus on NPIs to slow the
spread of the disease has been accompanied by vaccines and a growing acceptance and use
of rapid tests. At broadly similar points in time, novel strains of the virus have
started to pose additional challenges.

@@

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations and rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections with only one channel active,
the final level is always the highest in case of the vaccination campaign (orange
lines). The Shapley value decomposition shows that vaccinations contribute 16\% to the
cumulative difference between scenarios. Reasons for this are the slow start---it took
until March~24th until 10\% of the population had received their first vaccination, the
20\% mark was reached on April 19th---and the focus on older individuals. These groups
contribute less to the spread of the disease than others due to a lower number of
contacts. By the end of our study period, when first-dose vaccination rates reached
around 40\% of the population, the numbers of new cases would have started to decline.
It is important to note that the initial focus of the campaign was to prevent deaths and
severe disease. Indeed, the case fatality was rate considerably lower during the third
wave when compared to the second (4.4\% between October and February and 1.4\% between
March and the end of May).\comment[id=K]{This needs a source.}\comment[id=HM]{Didn't we
calculate that ourselves at some point?}

### 2021-07-13 src/paper/results/rapid_tests_statistics.tex
Went through paper once.

\begin{figure}[ht] % Share tested per day
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
      \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested}
      \caption{Share of the Population Doing a Rapid Test Because of Different Channels
      on a Given Day}
      \label{fig:rapid_test_demand_by_channel}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
      \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested_positive}
      \caption{Share of the Population Testing Positive Because of Different Channels
      on a Given Day}
      \label{fig:pos_rapid_tests_by_channel}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
      \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested_negative}
      \caption{Share of the Population Testing Negative Because of Different Channels
      on a Given Day}
      \label{fig:neg_rapid_tests_by_channel}
  \end{subfigure}
  \caption{Rapid Test Shares in the Population by Channel}
  \floatfoot{\noindent \textit{Note:}
    Rapid tests in the education setting are demanded by teachers (nursery, preschool and
    school) as well as pupils. After Easter the required frequency of tests is
    increased from once per week to twice per week. Work rapid tests are demanded by
    individuals that still have work contacts, i.e. do not work from home. The share of
    employers offering rapid tests increases over the time frame and the frequency of
    testing is also increased. Private tests are demanded by individuals for one of three
    reasons: having developed symptoms without access to a PCR test, having a household
    member that has tested positive or developed symptoms or having planned a weekly
    meeting with friends. The left figure shows the share of the population doing a
    rapid test on a given day. The middle figure shows the share of the population
    testing positive on a given day (true and false positives). The right figure shows
    the share of the population testing negative on a given day (true and false
    negatives).}
\end{figure}

>>>>

\begin{figure}[ht] % Share tested per day
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested}
        \caption{Share of the Population Doing a Rapid Test on a Given Day, by Channels}
        \label{fig:rapid_test_demand_by_channel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested_positive}
        \caption{Share of the Population Testing Positive on a Given Day, by Channels}
        \label{fig:pos_rapid_tests_by_channel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested_negative}
        \caption{Share of the Population Testing Negative on a Given Day, by Channels}
        \label{fig:neg_rapid_tests_by_channel}
    \end{subfigure}
    \caption{Rapid Test Shares in the Population by Channel}
    \floatfoot{\noindent \textit{Note:}
        Rapid tests in the education setting are demanded by teachers (nursery,
        preschool and school) as well as pupils. After Easter the required frequency of
        tests is increased from once per week to twice per week. Work rapid tests are
        demanded by individuals that still have work contacts, i.e. do not work from
        home. The share of employers offering rapid tests increases over the time frame
        and the frequency of testing is also increased. Private tests are demanded by
        individuals for one of three reasons: having developed symptoms without access
        to a PCR test, having a household member that has tested positive or developed
        symptoms or having planned a weekly meeting with friends. The left figure shows
        the share of the population doing a rapid test on a given day. The middle figure
        shows the share of the population testing positive on a given day (true and
        false positives). The right figure shows the share of the population testing
        negative on a given day (true and false negatives).}
\end{figure}
